Verifying Demonstrations

### 2018-03-16 paper/protocol.tex
Writes up more details of protocol (up to submission)

\NewCryptoScheme{\PRIVOscheme}{PRIVO}
\NewAlgorithm{\PRIVOsetup}{Setup}
\NewAlgorithm{\PRIVOreg}{Register}
\NewAlgorithm{\PRIVOjoin}{Join}
\NewAlgorithm{\PRIVOparticipate}{Participate}
\NewAlgorithm{\PRIVOsubmit}{Submit}

\NewCryptoEntity{\Alice}{A}
\NewCryptoEntity{\Bob}{B}
\NewCryptoEntity{\Carol}{C}

We now present \PRIVO, a protocol for securely and PRIvately Verifying PROtests.
The protocol consists of four phases: the setup, join, participation and 
submission phases.
We have several roles.
We have \iac{CA} who is responsible for a one-to-one mapping between a person's 
identity and a cryptographic key.
We have the protesters Alice (\(\Alice\)), Bob (\(\Bob\)) and Carol (\(\Carol\)) 
who want to participate in a given protest.

@@

@@

\emph{Registration: \(sk\gets 
    \Proto{\PRIVOreg[_P][spk]}{\PRIVOreg[_{CA}][ssk]}\).}
During the registration phase, each protester will generate a secret key and 
obtain a signature on it by the \ac{CA} --- without revealing it to the \ac{CA}.
Thus each protester will have a signed secret key, the \ac{CA} will issue only 
one signature per protester but will not know who has which key.
The protester chooses \(d, r\gets \ZZ_q\) uniformly randomly and sets \(M = g^d 
  Z^r\) and send \(M\) to the server.
The protester acts as prover and the \ac{CA} as verifier while they perform the 
following \ac{ZKPK} protocol: \(\PK[d,r][M = g^d Z^r]\).
If the proof succeeds, the \ac{CA} chooses \(a\gets \ZZ_q^*\) and sets \(A = 
  g^a\).
Then it forms the signature \(s = (A, B = A^y, Z_B = B^z = Z^{ay}, C = A^x 
  M^{axy})\) and sends it to the protester.
The protester verifies that the following equations hold:
\begin{align*}
  A &\neq 1 \\
  e(g, B) &= e(Y, A) \\
  e(g, Z_B) &= e(Z, B) \\
  e(g, C) &= e(X, A) e(X, B)^d e(X, Z_B)^r.
\end{align*}
Upon success, the protester uses \(sk = (s, d, r)\).

@@

@@

\begin{figure}
  \centering
  \footnotesize
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
        & cid\gets \Hash[\text{manifesto}], \\
        & pid\gets \ACprf[_{k_P}][cid] \\
      W\colon & t_s'\gets \TSget
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & pid \\
      P\leftrightarrow W\colon &
        \DBPK\mleft\{ (k_P) : \mright. \\
        & \qquad pid = \ACprf[_{k_P}][cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{ssk}][k_P]] \mright\} \\
      W\colon & wid\gets \ACprf[_{k_W}][pid], \\
        & wsig\gets \ACprf[_{k_W}][wid, t_s, t_s', l] \\
      W\to P\colon & (wid, t_s, t_s', l, wsig)
      \\[-1em]
      \noalign{\hfill Participation}
      \midrule
      \noalign{\hfill Submission}
      \\[-2em]
      W\colon & t_e\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]] \\
      P\colon & t_e\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]] \\
      W\to S\colon & (pid, wid, t_s, t_s', t_e, l, wsig, \pi_W),\quad 
      \text{where} \\
        & \pi_W = \SPK\mleft\{ (k_W) : \mright. \\
        & \qquad wid = \ACprf[_{k_W}][pid], \\
        & \qquad wsig = \ACprf[_{k_W}][wid, t_s, t_s', l], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{ssk}][k_W]]\mright\} \\
        & \qquad\qquad (pid, wid, t_s, t_s', l, wsig) \\
      P\to S\colon & (pid, wid, t_s, t_s', t_e, l, wsig, \pi_P),\quad 
      \text{where}\\
        & \pi_P = \SPK\mleft\{ (k_P) : \mright. \\
        & \qquad pid = \ACprf[_{k_P}][cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{ssk}][k_P]] \mright\} \\
        & \qquad\qquad (pid, wid, t_s, t_s', l, wsig)
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of of the Join, Participation and Submission phases of \PRIVO.\@
    The organizer \(O\) broadcasts the manifesto.
    \(P\), \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
  }%
  \label{fig:ProtocolOverview}
\end{figure}

>>>>

\NewCryptoScheme{\PRIVOscheme}{PRIVO}

We now present \PRIVO, a protocol for securely and PRIvately Verifying PROtests.
The protocol consists of four phases: the setup, join, participation and 
submission phases.
We have several roles.
We have \iac{CA} who is responsible for a one-to-one mapping between a person's 
identity and a cryptographic key.
We have the protesters who want to participate in a given protest.
A protester can assume three different roles:
\begin{enumerate*}
\item We have the \emph{organizer} who will simply write a manifesto for the 
  protest and spread to others.
\item A \emph{participant} participates in the protest (and asks witnesses to 
  vouch for his presence).
\item A \emph{witness} provides proofs to participants that state the 
  participant was indeed participating and the proofs are verifiable by third 
  parties.
\end{enumerate*}
In general, there is one organizer and every protester will act as both 
participant and witness.

@@

\NewAlgorithm{\PRIVOsetup}{Setup}

@@

\NewAlgorithm{\PRIVOreg}{Register}

\emph{Registration: \(sk\gets 
    \Proto{\PRIVOreg[_P][spk]}{\PRIVOreg[_{CA}][ssk]}\).}
During the registration phase, each protester will generate a secret key and 
obtain a signature on it by the \ac{CA} --- without revealing it to the \ac{CA}.
Thus each protester will have a signed secret key, the \ac{CA} will issue only 
one signature per protester but will not know who has which key.
The protester chooses \(k, r\gets \ZZ_q\) uniformly randomly and sets \(M = g^k 
  Z^r\) and send \(M\) to the server.
The protester acts as prover and the \ac{CA} as verifier while they perform the 
following \ac{ZKPK} protocol: \(\PK[k,r][M = g^k Z^r]\).
If the proof succeeds, the \ac{CA} chooses \(a\gets \ZZ_q^*\) and sets \(A = 
  g^a\).
Then it forms the signature \(\sigma = (A, B = A^y, Z_B = B^z = Z^{ay}, C = A^x 
  M^{axy})\) and sends it to the protester.
The protester verifies that the following equations hold:
\begin{align*}
  A &\neq 1 \\
  e(g, B) &= e(Y, A) \\
  e(g, Z_B) &= e(Z, B) \\
  e(g, C) &= e(X, A) e(X, B)^k e(X, Z_B)^r.
\end{align*}
Upon success, the protester uses \(sk = (\sigma, k, r)\).

@@

\emph{Creating a protest: the manifesto.}
The organizer will write a manifesto for the protest, \ie to capture the cause.
This manifesto is simply any intelligible text.
He will distribute this manifesto to people: on the Web, on placards, \etc.
If they agree, they will use it to join the protest.

\NewAlgorithm{\PRIVOjoin}{Join}

\emph{Joining participant: \((pid, t_s)\gets 
    \PRIVOjoin[_P][\text{manifesto}]\).}
A participant who wants to join the protest will use the manifesto to compute an 
identifier for the cause, \(cid\gets \Hash[\text{manifesto}]\).
Then this identifier is used to create the participant's protest-specific 
identifier, \(pid\gets \ACprf[_{sk}][cid]\) (in 
\cref{fig:ProofFig,fig:ProtocolOverview}).
More specifically, \(pid = g_T^{1/(k+cid)}\) (remember that \(sk = (\sigma, k, 
  r)\)).
The participant should also get a time-correlated random value from the 
time-stamping service, \(t_s\gets \TSget\).

\emph{Joining witness: \(t_s'\gets \PRIVOjoin_W\).}
The witness simply should simply get a time-correlated random value from the 
time-stamping service, \(t_s'\gets \TSget\).
(We do this for redundancy, the newest of \(t_s\) and \(t_s'\) will set the 
start of the time interval of creation for the proof share.).

\NewAlgorithm{\PRIVOparticipate}{Participate}
\NewAlgorithm{\PRIVOwitness}{Witness}

\emph{Participating: \(\pi\gets
    \Proto{\PRIVOparticipate[cid, sk_P]}{\PRIVOwitness[sk_W, spk]}\),}
The participant reblinds its signature \(\sigma\) on its secret key: choose 
\(r_1, r_2\gets \ZZ_q^*\) and let \(
  \hat\sigma = (\hat A = A^{r_1},
                \hat B = B^{r_1},
                \hat Z_B = Z_B^{r_1},
                \hat C = C^{r_1 r_2}).
\) (It is not necessary to compute a new \(\hat\sigma\) more than once per 
\(pid\).)
The participant sends \((pid, \hat\sigma)\) to the witness.
The witness verifies that
\begin{align*}
  \hat A &\neq 1 \\
  e(g, \hat B) &= e(Y, \hat A) \\
  e(g, \hat Z_B) &= e(Z, \hat B).
\end{align*}
Both the participant and the witness compute
\begin{align*}
  v &= e(g, \hat C) \\
  v_x &= e(X, \hat A) \\
  v_{xy} &= e(X, \hat B) \\
  v_{xy}' &= e(X, \hat Z_B).
\end{align*}
Then they run the following \ac{DBPK} with the participant as the prover and the 
witness as the verifier:
\begin{multline*}
  \DBPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
    pid = g_T^{1/(k+cid)} \right\}.
\end{multline*}

\NewAlgorithm{\PRIVOsubmit}{Submit}

@@

\begin{figure}
  \centering
  \footnotesize
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
        & cid\gets \Hash[\text{manifesto}], \\
        & pid\gets \ACprf[_{sk_P}][cid] \\
      W\colon & t_s'\gets \TSget
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & pid \\
      P\leftrightarrow W\colon &
        \DBPK\mleft\{ (sk_P) : \mright. \\
        & \qquad pid = \ACprf[_{sk_P}][cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{ssk}][sk_P]] \mright\} 
        \\
      W\colon & wid\gets \ACprf[_{sk_W}][pid], \\
        & wsig\gets \ACprf[_{sk_W}][wid, t_s, t_s', l] \\
      W\to P\colon & (wid, t_s, t_s', l, wsig)
      \\[-1em]
      \noalign{\hfill Participation}
      \midrule
      \noalign{\hfill Submission}
      \\[-2em]
      P\colon & t_e\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]] \\
      W\colon & t_e'\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]] \\
      W\to S\colon & (pid, wid, t_s, t_s', t_e, l, wsig, \pi_W),\quad 
      \text{where} \\
        & \pi_W = \SPK\mleft\{ (sk_W) : \mright. \\
        & \qquad wid = \ACprf[_{sk_W}][pid], \\
        & \qquad wsig = \ACprf[_{sk_W}][wid, t_s, t_s', l], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{ssk}][sk_W]]\mright\} \\
        & \qquad\qquad (pid, wid, t_s, t_s', l, wsig) \\
      P\to S\colon & (pid, wid, t_s, t_s', t_e, l, wsig, \pi_P),\quad 
      \text{where}\\
        & \pi_P = \SPK\mleft\{ (sk_P) : \mright. \\
        & \qquad pid = \ACprf[_{sk_P}][cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{ssk}][sk_P]] \mright\} 
        \\
        & \qquad\qquad (pid, wid, t_s, t_s', l, wsig)
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of of the Join, Participation and Submission phases of \PRIVO.\@
    The organizer \(O\) broadcasts the manifesto.
    The protester \(P\), witness \(W\) and their computations are as in 
    \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
  }%
  \label{fig:ProtocolOverview}
\end{figure}
